Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Lemmas.tex
fix to lemma 4, edits to thm 3

\begin{rlemma}{Lemma}{\ref{lem:phase-length}}
For any $s\geq 3$, the expected length of phase $s$ is at most
$\ARMNUM \cdot \log(s)$ time steps.
\end{rlemma}

\begin{proof}
Let $S$ be the set of arms that have been pulled at most
$s$ times at the start of phase $s$.
Thus, phase $s$ has ended when each $i \in S$ has been pulled at least once.
Consider any time step $t$.
If $S$ contains at least one payment-eligible arm $i$,
then some payment-eligible arm will be pulled with probability 1,
and every payment-eligible arm is in $S$.
In particular, the size of $S$ decreases with probability 1.
If $S$ contains no payment-eligible arm,
then by definition of payment-eligibility,
each arm $i \in S$ has probability at least $1/\log(s)$ of being pulled.
In particular, the size of $S$ decreases with probability at least $1/\log(s)$.

In either case, the expected number of time steps until
$|S|$ decreases is at most $\log s$,
so the expected number of steps until $S$ is empty is at most
$\ARMNUM \cdot \log(s)$.
\end{proof}

>>>>

\begin{rlemma}{Lemma}{\ref{lem:phase-length}}
For any $s\geq 3$, the expected length of phase $s$ is at most
$\ARMNUM \cdot \log(s)$ time steps.
\pfedit{
Moreover, for any set of types $A$, the expected number of times that 
an agent with a type in $A$ appears in a phase $s$ is at most 
$f(A) \cdot \ARMNUM \cdot \log(s)$,
where $f(A) := \Prob[\AgV \sim \AgentDist]{\ArmV \in A}$.
}
\end{rlemma}

\begin{proof}
\pfedit{
We show the second claim for general $A$, which implies the first claim by taking $A$ to be the support of $\AgentDist$.

Fix a phase $s$ and let $S_t$ be the set of arms that have been pulled at most $s$ times by time $t$.  Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$) and the time $t$ when $S_t$ first contains $m$ elements.  The phase ends when $S_t$ contains no elements, i.e., $\tau_0 = t_{s+1}$.
We consider the expected number of pulls during times $[\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.

Consider a counter starting from $0$ at time $\tau_m$ that increments each time an agent arrives with a type in $A$, and that is stopped the first time an arm in $S_t$ is pulled.
For any stopping time $t \in [\tau_m, \tau_{m-1})$, 
the conditional probability that the counter increments
given the history of pulls, payments, and observations at time $t$ 
is $f(A)$.
The conditional probability that the counter is stopped by that agent's pull is at least $1/\log(s)$.  To see this, consider two cases.  In the first case, there is at least one payment eligible arm, in which case the principal incentives an arm in $S_t$.  In the second case, there are no payment eligible arms.  
Then, by definition of payment-eligibility,
each arm $i \in S_t$ has conditional probability at least $1/\log(s)$ of being pulled.

The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$, and is otherwise identical.  (This can be shown more formally via a coupling argument.)
Let $V_\ell$ be the conditional expectation of this second counter's value when it is stopped,
given that its current value is $\ell$ and it has not been stopped.  Observe that $V_\ell = \ell + V_0$.
Enumerating outcomes (either the counter increments or not; either it stops or it continues) provides $V_0 = f(A)\frac1{\log(s)} + f(A) (1-\frac1{\log(s)}) V_1 + (1-f(A))(1-\frac1{\log(s)}) V_0$.
Using $V_1 = 1 + V_0$ simplifies this to 
$V_0 = f(A) + (1-\frac1{\log(s)}) V_0$.
Noting $V_0$ is finite and solving for $V_0$ provides
$V_0 = f(A) \log(s)$.
Thus, the conditional expected number of pulls (given the history at time $\tau_m$) by an agent with a type in $A$ during times in $[\tau_m, \tau_{m-1})$ is no more than $f(A) \log(s)$.

We may write the total number of pulls by agents with types in $A$ during phase $s$ as a sum of this quantity over $m$ ranging from $|S_{t_s}|$ down to 1.  Noting that $|S_{t_s}| \le N$ and taking the expectation of this sum shows the claim. 
}
\end{proof}
